Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-23 Papers/ms.tex
Small clarification
Two more paragraphs in the conclusion

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within the SIE$+\gamma$ family. In fact, some of the posterior
samples obtained contain massive substructures outside of the image, which
could be modelling higher-order effects of the environment beyond what is
captured by the simple external shear model.
One way of further investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.
Another option which we defer to future work is to implement a more flexible
model (such as a concentric mixture of concentric elliptical lenses). This
result is consistent with that of \citet{2008MNRAS.388..384D}, who found a slight preference for an elliptical power law profile over the SIE
(which is a specific case of an elliptical power law).

@@

As a proof of concept, we demonstrated the successful recovery of a single
substructure from simulated data for which all of the model assumptions were
true. We then applied the method to an image of the Cosmic Horseshoe system
and found mild evidence in favour of the existence of a substructure, or at
the very least, a departure from a simple SIE+$\gamma$ lens profile.

>>>>

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within the SIE$+\gamma$ family. In fact, some of the posterior
samples obtained contain massive substructures outside of the image, which
could be modelling higher-order effects of the environment beyond what is
captured by the simple external shear model. This is one way of violating
the SIE$+\gamma$ assumption, and another is simply to have a different projected
density profile.
One way of further investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.
Another option which we defer to future work is to implement a more flexible
model (such as a concentric mixture of concentric elliptical lenses). This
result is consistent with that of \citet{2008MNRAS.388..384D}, who found a slight preference for an elliptical power law profile over the SIE
(which is a specific case of an elliptical power law).

@@

As a proof of concept, we demonstrated the successful recovery of a single
substructure from simulated data for which all of the model assumptions were
true. We then applied the method to an image of the Cosmic Horseshoe system
and found mild evidence in favour of the existence of a substructure, or at
the very least, a departure from a simple SIE+$\gamma$ lens profile. The
main output of our method is a set of posterior samples, each representing
a plausible scenario for the lens and the source given the data
and the assumed prior information. These samples can be displayed as a movie,
which is a very useful method for intuitively understanding the remaining
uncertainty. Any posterior summaries of interest can be
produced from the samples, but the interpretation of many of these summaries
is not necessarily straightforward. We have suggested that the
posterior expectation of the empirical measure of substructure positions is
one of the most helpful summaries.

The model assumptions used in this paper are fairly simple. In future work we
intend to generalise the smooth lens model beyond the overly simplistic
SIE+$\gamma$ model, and to generalize the model to multi-band data. Applications
to other systems are also forthcoming, as well as variants on the model using
different conditional priors for the substructure properties given the
hyperparameters.
